Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-06-01 neurips-20/cvx-flats.tex
intro, notation, calibration pass

\section{Introduction}\label{sec:intro}
\raf{General comment: see if you can make the intro less of an explanation to someone who has never heard of consistency, etc, and more of a ``reminder'' and recap of what's been going on in the field, culminating in the gap between what is out there and what we would like to know -- the gap that we fill}
\raf{General style: see if you can make the writing sharper, with less passive voice.  See if you can channel some Hemmingway and boil each sentence down to the key point.}
\jessie{Alright, I tried...}
In supervised machine learning, one often makes predictions about future outcomes by minimizing a surrogate loss on training data.
The use of a surrogate is often necessary for one of two reasons: the target loss does not satisfy some ``niceness'' conditions that we desire, or there is no target loss.
When given a target loss, a surrogate should yield good statistical guarantees; informally, we want low surrogate risk to imply low target risk.
%A good surrogate should yield bounds on the excess risk so that optimal predictions for the surrogate can be linked to optimal predictions for a target (possibly discrete) loss with bounded excess error, regardless of the underlying data distribution.
%\raft{Style example: ``we want low surrogate risk to mean low target risk.''}
In continuous estimation settings, one often starts with a statistic of the data they would like to estimate instead of a target loss, such as the conditional expected value.
We are able to generalize consistency to make sense in target loss-less contexts (Definition~\ref{def:consistent-prop}).
%For example, if one wants to estimate the $\alpha$-quantile, they can do so by minimizing pinball loss over their data, but it is often unclear \emph{why} pinball loss is good for this prediction task.
\raft{I think few ML people know anything about pinball loss... I think we should de-emphasize the continuous setting in the intro, and include it in passing.}\jessie{Removed the sentence, but probably want to at least allude to it?}
The statistical guarantees we desire from a surrogate are \emph{consistency}: a precursor to excess risk bounds and rates.
%\raft{we desire \emph{consistency}, a precursor to excess risk bounds and rates}
We are particularly interested in consistent \emph{and convex} surrogates in which any sequence of hypotheses converging to the optimal prediction can be linked to a sequence that converges to either the correct prediction for the discrete loss or statistic value, depending on the setting. 
We would also like our surrogate losses to be efficient in the dimension of the input, as this is one potential source of significant computational speedup.

%\raf{Maybe start with ``in this paper, we'' or similar, and recap the high-level contributions.  E.g. ``Our results give two contributions to this field.  First, .....  Second, .....''  Something like that before going into the theorems.}
Our results contribute two major findings to this field.
First, we show that indirect property elicitation is a necessary condition for consistency (Theorem~\ref{thm:consistent-implies-indir-elic}).
This allows us to use property elicitation to bound the minimum dimension needed to construct a consistent convex surrogate.
Previous lower bounds on the dimension of a consistent convex surrogate for a given task have been considered in one of four settings: whether one is given a target loss or not, and whether one is making a continuous or discrete prediction.
\raft{Cleaned up this prev sentence} \jessiet{Noted... much better how it is now.}
Our second main contribution (Theorem~\ref{thm:cvx-flats}) is general enough to yield bounds across all four settings, and is the first result to our knowledge to handle this generality.

@@

\raf{I'd suggest discussing general stuff here ($\X\times\Y$, etc) and moving more specific stuff to a more contextual spot --- e.g. property notation in that subsection, feature space etc in 2.0, $R_L$ to where we use it, etc.  We could keep notation like $\supp,\affhull,2^\R$ in a terse paragraph just before 2.1}
\raf{Do we use $L(u;p)$ much?  It's $L(u,p)$ below.  I'd prefer to avoid it unless we really use it a ton.}\jessie{We primarily use $L(u;p)$. It was just a typo in this introduction of regret.  I don't mind changing it, but I like the semicolon.  I think that might be Bo's class influencing me haha.  My preferences aren't super strong one way of the other here.}

We consider learning from pairs in $\X \times \Y$, for some \emph{feature space} $\X$ and \emph{outcome space} $\Y$.
The goal is to produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} (or prediction space) $\R$, which may be different from $\Y$.
For example in ranking problems, $\R$ may be all $n!$ permutations over the $n$ outcomes forming $\Y$.

In general, we use $\ell: \R \times \Y \to \reals$ to denote a \emph{target loss} where the goal is to minimize expected loss, $\E \ell(f(X),Y)$ for pairs $X,Y$ drawn from some distribution.
We use $L: \reals^d \times \Y \to \reals$ to denote a \emph{surrogate} loss, and typically denote a surrogate prediction with $u \in \reals^d$.
A loss $\ell$ is \emph{discrete} if $|\Y|$ and $|\R| < \infty$, and a surrogate $L$ is \emph{convex} if it is convex in the prediction space for every outcome $y \in \Y$.

@@

\bo{What about introducing the quadrants here? Something like: ``Instead of a target loss, in some estimation problems, one is given a target \emph{property}: [say what a property is]. The goal is to learn $f$ that approximately outputs the property on the conditional distribution given $x$. Example: mean estimation, etc..."}
\jessie{This preceded the property elicitation notation before, which got moved to 2.3... don't think this comment still applies, but not sure?}
\raf{Isn't that what we do next anyway?  I think it's nice in 2.1}

@@

\bo{Citation help appreciated!} \jessie{\cite{fisher1922mathematical,zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex} -- these are the ones I know of that discuss consistency in slightly various forms.  I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is \emph{consistency}, which roughly means that minimizing $L$-loss corresponds to solving the target problem of interest.
\raft{Suggest ``target'' instead of original, based on Steinwart -- I think it's really clear that way}
One measure of difficulty of a learning problem is the dimension $d$ of consistent surrogate losses.
We want to lower-bound this dimension for a given learning problem.
\bo{Maybe something here about how consistency means different things in different settings, so lower-bounding it with a single general technique seems tricky. Then the bullet points explain the different settings.} \jessie{Adding a few sentences to try to address this... probably needs to be pared down.}
Consistency, which we formalize in Section~\ref{sec:consis-implies-indir}, is not very tractable.
Throughout the literature, consistency is defined in many subtlely different ways; some papers (e.g.\,\cite{ramaswamy2016convex,ramaswamy2018consistent}) refer to consistent \emph{algorithms} while others (e.g.\,\cite{bartlett2006convexity,tewari2007consistency}) refer to consistent \emph{losses}.
Even more confusing is the slight difference between considering consistency based on the sequence of functions learned from trianing on $m$ samples as opposed to learning over any general sequence of functions.
In general, consistency relies on both a surrogate and target loss, and until now, it has been unclear how to define consistency without a target loss. 
Ideally, we would have a more useful condition that could apply to all of the following settings:
\begin{itemize}
  \item The original prediction space is either \textbf{discrete}, e.g. a classification problem; or it is \textbf{continuous}, e.g. a regression or estimation problem.
  \item The original prediction problem is given either directly by a \textbf{loss} $\ell$, for which $L$ should be a surrogate; or it is given by a \textbf{property} or statistic that we would like to estimate, for example the mean, variance, or entropy of the conditional distributions $D_x$.
\end{itemize}
We informally call the combinations of these characteristics the ``four quadrants'' of supervised learning problems.
For exmaple, one quadrant has problems that are continuous and specified by a property $\gamma$.
An example learning problem in this quadrant would be mean estimation: hypotheses should map $x$ to the mean of the conditional distribution $D_x$

In particular, a highly-studied case consists of discrete prediction spaces along with original losses $\ell$, for example, surrogates for 0-1 loss.
Here a notable more-tractable condition is \emph{calibration}, which we discuss next.

>>>>

\section{Introduction}\label{sec:intro}
\raf{General comment: see if you can make the intro less of an explanation to someone who has never heard of consistency, etc, and more of a ``reminder'' and recap of what's been going on in the field, culminating in the gap between what is out there and what we would like to know -- the gap that we fill}
\raf{General style: see if you can make the writing sharper, with less passive voice.  See if you can channel some Hemmingway and boil each sentence down to the key point.}
\jessie{Alright, I tried...}
In supervised machine learning, one often makes predictions about future outcomes by minimizing a surrogate loss on training data.
\bo{Reworded slightly.}
The use of a surrogate is often necessary for one of two reasons: the target loss does not satisfy some ``niceness'' conditions that we desire, or the goal is to estimate some statistic rather than minimize some target loss.
When given a target loss, a surrogate should yield good statistical guarantees; informally, we want low surrogate risk to imply low target risk.
%A good surrogate should yield bounds on the excess risk so that optimal predictions for the surrogate can be linked to optimal predictions for a target (possibly discrete) loss with bounded excess error, regardless of the underlying data distribution.
%\raft{Style example: ``we want low surrogate risk to mean low target risk.''}
In continuous estimation settings, one often starts with a statistic of the data they would like to estimate instead of a target loss, such as the conditional expected value.
We are able to generalize consistency to make sense in target loss-less contexts (Definition~\ref{def:consistent-prop}).
%For example, if one wants to estimate the $\alpha$-quantile, they can do so by minimizing pinball loss over their data, but it is often unclear \emph{why} pinball loss is good for this prediction task.
\raft{I think few ML people know anything about pinball loss... I think we should de-emphasize the continuous setting in the intro, and include it in passing.}\jessie{Removed the sentence, but probably want to at least allude to it?}
The statistical guarantees we desire from a surrogate are \emph{consistency}: a precursor to excess risk bounds and rates.
%\raft{we desire \emph{consistency}, a precursor to excess risk bounds and rates}
We are particularly interested in consistent \emph{and convex} surrogates in which any sequence of hypotheses converging to the optimal prediction can be linked to a sequence that converges to either the correct prediction for the discrete loss or statistic value, depending on the setting. 
We would also like our surrogate losses to be efficient in the dimension of the input, as this is one potential source of significant computational speedup.

%\raf{Maybe start with ``in this paper, we'' or similar, and recap the high-level contributions.  E.g. ``Our results give two contributions to this field.  First, .....  Second, .....''  Something like that before going into the theorems.}
\bo{Reworded to avoid saying our findings are major -- some people won't like that.}
Our results make two contributions to this field.
First, we show that indirect property elicitation is a necessary condition for consistency (Theorem~\ref{thm:consistent-implies-indir-elic}).
This allows us to use property elicitation to bound the minimum dimension needed to construct a consistent convex surrogate.
Previous lower bounds on the dimension of a consistent convex surrogate for a given task have been considered in one of four settings: whether one is given a target loss or not, and whether one is making a continuous or discrete prediction.
Our second main contribution (Theorem~\ref{thm:cvx-flats}) is general enough to yield bounds across all four settings, and is the first result to our knowledge to handle this generality.

@@

\bo{I think this organization is great now!}

%\raf{I'd suggest discussing general stuff here ($\X\times\Y$, etc) and moving more specific stuff to a more contextual spot --- e.g. property notation in that subsection, feature space etc in 2.0, $R_L$ to where we use it, etc.  We could keep notation like $\supp,\affhull,2^\R$ in a terse paragraph just before 2.1}
\raf{Do we use $L(u;p)$ much?  It's $L(u,p)$ below.  I'd prefer to avoid it unless we really use it a ton.}\jessie{We primarily use $L(u;p)$. It was just a typo in this introduction of regret.  I don't mind changing it, but I like the semicolon.  I think that might be Bo's class influencing me haha.  My preferences aren't super strong one way of the other here.}

We consider learning from pairs in $\X \times \Y$, for some \emph{feature space} $\X$ and \emph{outcome space} $\Y$.
A learning algorithm must produce a hypothesis $f: \X \to \R$, for some \emph{prediction space} (or prediction space) $\R$, which may be different from $\Y$.
For example in ranking problems, $\R$ may be all $n!$ permutations over the $n$ outcomes forming $\Y$.

In general, we use $\ell: \R \times \Y \to \reals$ to denote a \emph{target loss} where the goal is to minimize expected loss, $\E ~ \ell(f(X),Y)$ for pairs $X,Y$ drawn from some distribution.
We use $L: \reals^d \times \Y \to \reals$ to denote a \emph{surrogate} loss, and typically denote a surrogate prediction with $u \in \reals^d$.
A loss $\ell$ is \emph{discrete} if $|\Y|$ and $|\R| < \infty$, and a surrogate $L$ is \emph{convex} if it is convex in the prediction space for every outcome $y \in \Y$.

@@

%\bo{What about introducing the quadrants here? Something like: ``Instead of a target loss, in some estimation problems, one is given a target \emph{property}: [say what a property is]. The goal is to learn $f$ that approximately outputs the property on the conditional distribution given $x$. Example: mean estimation, etc..."}
%\jessie{This preceded the property elicitation notation before, which got moved to 2.3... don't think this comment still applies, but not sure?}
%\raf{Isn't that what we do next anyway?  I think it's nice in 2.1}

@@

\bo{Rewrote this, Mon Jun 1 a.m.}
%\bo{Citation help appreciated!} \jessie{\cite{fisher1922mathematical,zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex} -- these are the ones I know of that discuss consistency in slightly various forms.  I believe the definition we run with is most similar to \cite{ramaswamy2016convex}.}
A basic requirement of surrogate losses $L: \reals^d \times \Y \to \reals$ is \emph{consistency}, which roughly means that minimizing $L$-loss corresponds to solving the target problem of interest.
We consider two kinds of consistency.
In the first, we are given a \textbf{target statistic} such as the conditional variance, as in classical statistics~\citep{fisher1922mathematical}.
Here we will define $L$ to be consistent (Definition \bo{TODO}) if minimizing $L$ and applying a link function yields estimates converging to the correct value, by some measure.
In the second, we are given a \textbf{target loss} $\ell$ and we define $L$ to be consistent (Definition \bo{TODO}) if minimizing $L$ and applying a link yields hypotheses minimizing $\ell$.
This kind follows much of the machine learning literature~\citep{zhang2004statistical,bartlett2006convexity,tewari2007consistency,steinwart2007compare,ramaswamy2016convex}.

It is also useful to distinguish between two domains: a \textbf{discrete} target prediction space, e.g. a classification problem; versus a \textbf{continuous} one, e.g. a regression or estimation problem.
We informally refer to the four resulting cases -- target statistic versus target loss and discrete versus continuous predictions -- as the ``four quadrants'' of supervised learning problems.

The goal of this paper is to give lower bounds on the dimension $d$ of consistent surrogate losses.
A priori, it is not necessarily clear that compatible definitions of consistency could be given for both target statistics and target losses; for this we turn to our key tool of \emph{property elicitation}.
This technique will then allow us to prove lower bounds across all four quadrants.
In prior work, most research on this problem focuses on the quadrant of target losses and discrete predictions. \bo{cite?}
Moreover, definitions of consistency itself are relatively intractable and opaque, so this literature often focuses on a weaker condition called calibration.
